Figures

### 2019-04-24 figures/02_hierarchical_demo.Rmd
solve mystery rendering issue

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 5, fig.height = 5)
source("../scripts/99_utils.R")
```

```{r hu4_n, echo=FALSE, message=TRUE, eval=TRUE}
# setwd("figures")
ids <- test <- readRDS("../data/dt.rds") %>%
  group_by(hu4_zoneid) %>% 
  tally()

@@

# hist(hu4$n, n = 20)
# table(as.character(dt$hu4_zoneid))
```

```{r 02_hierarchical_demo, fig.height=3, echo=FALSE}
library(tidyr)
library(LAGOSNE)

@@

plot_grid(
  ggplot(data = dt, aes(x = ag_pct, y = tp, color = hu4_zoneid, alpha = n)) + 
    # geom_point() +
    geom_line(stat = "smooth", method = lm, se = FALSE, aes(alpha = n))  +
    geom_smooth(aes(group = 1), method = lm, se = FALSE, 
                color = "black", linetype = "dashed") +
    # scale_y_log10() + scale_x_log10() +
    theme(legend.position = "") +
    labs(x = "Ag. LULC (pct, NLCD 2011)", 
         y = "TP")  +
    scale_y_continuous(breaks = seq(0, 250, by = 50), limits = c(0, 300)),
  ggplot() +
    geom_sf(data = hu4, aes(fill = n_cat)) +
    # geom_text(data = coords, aes(x = x, y = y, label = ZoneID)) +   
    theme_minimal() + 
    theme(legend.position = "bottom", 
          axis.title = element_blank(), 
          legend.title = element_blank()) + 
    scale_fill_manual(values = colors, levels(hu4$n_cat)), 
  rel_heights = c(0.6, 1), labels = "AUTO"
)
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 6.5, fig.height = 4.5)
# setwd("figures")
source("../scripts/99_utils.R")
```

```{r 02_hierarchical_demo, echo=FALSE, message=TRUE, eval=TRUE}
# setwd("figures")
ids <- test <- readRDS("../data/dt.rds") %>%
  group_by(hu4_zoneid) %>% 
  tally()

@@

# hist(hu4$n, n = 20)
# table(as.character(dt$hu4_zoneid))

@@

cowplot::plot_grid(
  ggplot(data = dt, aes(x = ag_pct, y = tp, color = hu4_zoneid, alpha = n)) + 
    # geom_point() +
    geom_line(stat = "smooth", method = lm, se = FALSE, aes(alpha = n))  +
    geom_smooth(aes(group = 1), method = lm, se = FALSE, 
                color = "black", linetype = "dashed") +
    # scale_y_log10() + scale_x_log10() +
    theme(legend.position = "") +
    labs(x = "Ag. LULC (pct, NLCD 2011)", 
         y = "TP")  +
    scale_y_continuous(breaks = seq(0, 250, by = 50), limits = c(0, 300)),
  ggplot() +
    geom_sf(data = hu4, aes(fill = n_cat)) +
    # geom_text(data = coords, aes(x = x, y = y, label = ZoneID)) +
    theme_minimal() +
    theme(legend.position = "bottom",
          axis.title = element_blank(),
          legend.title = element_blank()) +
    scale_fill_manual(values = colors, levels(hu4$n_cat)),
  rel_heights = c(0.6, 1), labels = "AUTO"
)
```
